### 2022-09-27 README.Rmd
binder fix - attempt 1
update runtime

<!--[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio)--> 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)

<!-- DOI badge: [![DOI](.svg)](repo link) -->

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.pdf`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio) 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)
![Current version](https://img.shields.io/github/v/release/bbartholdy/byoc-starch?label=version)
<!-- DOI badge: [![DOI](.svg)](repo link) -->

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/refs/heads/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.pdf`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console
